---
title: "Cyclistic Marketing"
author: "Cherrie D. Cosby"
date: "2023-08-29"
output: html_document
---
Hello, I'm Cherrie Cosby. My journey into the world of computers was ignited by an insatiable curiosity that led me to dive deep into learning. This journey has taken me from being a contract software specialist to becoming a skilled data analyst. My expertise encompasses a wide range of sectors, from manufacturing to marketing, where I've skillfully blended my understanding of business dynamics with my prowess in software.
Throughout my career, I've spearheaded initiatives that have not only amplified revenues but also streamlined expenditures. I'm deeply driven by the prospect of driving innovation at the intersection of technology and business. I'm enthusiastic about lending my multidisciplinary insights to pioneering projects that have the potential to redefine norms.
My toolkit is well-equipped with VBA, SQL, R, Git, Python, and Tableau. These tools enable me to navigate complex challenges with finesse and creativity. I'm excited about the opportunity to collaborate and pave fresh pathways in this dynamic and thrilling realm. If you're as excited about the future of technology and business as I am, let's join forces and make remarkable strides together!
## Introduction GAC_Cyclistic_project
Project Overview

Welcome to the GAC_Cyclistic_project – a project focused on Cyclistic's 
marketing strategies to convert casual riders into annual members. Cyclistic is a 
bike share program in Chicago, boasting a fleet of 5,824 bikes across 692 docking 
stations. With diverse bike categories, styles, and pricing plans, Cyclistic caters 
to a wide range of riders – from leisure cyclists to daily commuters.

This project aims to delve into the behaviors of both annual members and 
casual riders, revealing valuable insights that will inform our strategic 
marketing approaches. Through the analysis of historical bike trip data 
and the utilization of tools such as Excel, VBA, PostgreSQL, R, and 
Tableau, we seek to answer crucial questions:

How do annual members and casual riders utilize Cyclistic bikes differently?
What are the key distinctions in usage patterns between these two groups?
What motivates casual riders to consider becoming annual members?
How can digital media play a role in converting casual riders into committed members?

Our motivation for undertaking this project is rooted in a passion for business 
analytics and a desire to contribute to the transformation of urban mobility. 
By optimizing Cyclistic's annual membership program, we strive to promote sustainable 
and eco-friendly transportation while providing a seamless and rewarding experience for riders.

Target Audience
The primary audience for this project is prospective employers, recruiters, and 
fellow data enthusiasts who seek to understand the practical application of data 
analysis in real-world scenarios. Our goal is to showcase a professional and 
skillful approach to business analytics, providing a tangible example of data-driven 
decision-making.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Install packages
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("dplyr")
install.packages(readr)
install.packages("tidyr")
install.packages("stringr")
install.packages("lubridate")
install.packages("rmarkdown")


# Load packages
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(lubridate)
library(rmarkdown)


<!-- Data Loading -->
<div class="custom-block">
# Load data 
error_free_records <-read.csv(“D:/CSV for R/error_free_records.csv”)
holiday_weather_merge <-read.csv(“D:/CSV for R/holiday_weather_merge.csv”)
This data is preprocessed, clean, and ready for analysis. To follow the steps taken to get to this point, please refer to the documentation available in my GIT repo ("<a href="https://github.com/CosbyCD/GAC_Cyclistic_project/preprocessing.md">https://github.com/CosbyCD/GAC_Cyclistic_project/preprocessing.md</a>") which walks you through from downloading the raw data into a finished product ready for use in R.
</div>

# Create segments based on member_casual column
```{r}
segmented_data <- error_free_records%>%
  dplyr::group_by(member_casual)%>%
  dplyr::summarise(average_ride_length = mean(ride_length, na.rm = TRUE))



# Create a bar plot using the loaded ggplot2 package
ggplot(data = segmented_data, aes(x = member_casual, y = average_ride_length)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Average Ride Length by Member Type",
       x = "Member Type", y = "Average Ride Length")
